Abstract Data Type Inference

### 2015-03-23 related.tex
Added note for related work.
More related work.

Inference of symbolic abstract data types is a recently-pertinent problem
arising from the the emergence of efficient symbolic refinement-checking
algorithms~\cite{conf/popl/BouajjaniEEH15, conf/pldi/EmmiEH15} which require
symbolic, logical representations of ADT specifications. Though approaches
based on the explicit enumeration of execution
linearizations~\cite{journals/jpdc/WingG93, conf/pldi/BurckhardtDMT10,
conf/asplos/BurnimNS11, conf/kbse/ZhangCW13} do not require symbolic ADT
representations, and work directly with given reference implementations, these
approaches are intractable, since the number of linearizations is exponential
in execution length.

@@

>>>>

Inference of symbolic abstract data types is a recently-pertinent problem
arising from the the emergence of efficient symbolic refinement-checking
algorithms~\cite{conf/popl/BouajjaniEEH15, conf/pldi/EmmiEH15} which require
symbolic, logical representations of ADT specifications. Though approaches
based on the explicit enumeration of execution
linearizations~\cite{journals/jpdc/WingG93, conf/pldi/BurckhardtDMT10,
conf/asplos/BurnimNS11, conf/kbse/ZhangCW13} do not require symbolic ADT
representations, and work directly with given reference implementations, these
approaches are intractable as they elaborate an exponential\footnote{The number
of possible linarizations is exponential in execution length.} number of
linearizations.

@@

The idea of inferring minimal finite representations of otherwise-infinite sets
of implementation behaviors has also been proposed as an optimization to reduce
the impact of state-space explosion in compositional
verification~\cite{journals/ase/GiannakopoulouPB05}. This approach is based on
learning minimal automata for regular languages, and requires the
implementation of both language membership and equivalence
queries~\cite{journals/iandc/Angluin87}. In our setting, it is unclear whether
ADT implementations may admit regular characterizations in general, and
furthermore how to automatically discharge language equivalence queries between
candidate automata and the source code of reference implementations.
